---
title: "Fiddler crab exercises"
format: html
editor: visual
execute:
  warning: false
  message: false
  echo: false
---

## Introduction

The data used in this report includes data on 25 to 37 adult male fiddler crabs (Atlantic marsh fiddler crab, Minuca pugnax (formerly Uca pugnax)) from 13 marshes on the Atlantic coast of the United States in summer 2016. The locations sampled spanned more than 12 degrees of latitude, from northeast Florida to northeast Massachusetts. Here we analyze carapace width by site and latitude in investigation of Bergmann's rule.

**Citations:** Johnson, D. 2019. Fiddler crab body size in salt marshes from Florida to Massachusetts, USA at PIE and VCR LTER and NOAA NERR sites during summer 2016. ver 1. Environmental Data Initiative. https://doi.org/10.6073/pasta/4c27d2e778d3325d3830a5142e3839bb (Accessed 2021-05-27).

Johnson DS, Crowley C, Longmire K, Nelson J, Williams B, Wittyngham S. The fiddler crab, Minuca pugnax, follows Bergmann's rule. Ecol Evol. 2019;00:1--9. https://doi.org/10.1002/ece3.5883

```{r}
library(tidyverse)
library(lterdatasampler)
library(kableExtra)
```

## Graph

```{r}
#| fig-cap: "Figure 1. Carapace width is observed to be greater at higher latitudes."

ggplot(data = pie_crab,
       aes(x = latitude,
           y = size)) +
  geom_point() +
  geom_smooth(method = lm,
              col = 'deeppink3') +
  theme_light() +
   theme(text = element_text(family = "Courier",
                                  size = 11,
                                  face = "bold"),
         axis.text = element_text(size = 9),
         panel.grid.minor.x = element_blank(),
         panel.grid.major.x = element_blank(),
         panel.grid.minor.y = element_blank(),
         panel.grid.major.y = element_blank()) +
  labs(x = "Latitude (degree)",
        y = "Carapace width (mm)",
        title = "Carapace width by latitude")


  
```

## Table

```{r}
pie_crab_summary <- pie_crab %>%
  group_by(site) %>%
  summarize(mean_width = round(mean(size, na.rm = TRUE), 2),
            sd_width = round(sd(size, na.rm = TRUE), 2),
            sample_size = n())
```

```{r}
pie_crab_summary %>%
  kable(col.names = c("Sites",
                      "Mean Width (mm)", 
                      "Standard Deviations for Width (mm)",
                      "Sample Size (n)")) %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE)
```
